Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-06 paper/paper.tex
pass intro
quick pass

@@

Finally, \tname{} ranks the inferred rules according to heuristics
extracted from a database of existing \tname{} rules. One example
heuristic is \Fix{...}. Instead of traffic, this step looks for the
structure of existing rules. The list below shows the rule options for
the five shortest rules \tname{} produces for this attack.

\Mar{<~ Lucas/Guilheme, há algo o que remover? talvez ``window:64''?
  Qual a correspondencia de ``flags:S,12'' com ``flags:S''? Por favor,
  respondam isto logo.}  \Gui{}

\subsection{Active Reconnaissance}

@@

Active reconnaissance is a method used by malicious individuals to
gather information about vulnerabilities from a computing system. The
most common approach is to ``scan'' open ports to discover
vulnerabilities. Active reconnaissance is a preliminary step towards
an attack that actually exploits the system. A Ping Scan is a very
common type of port scan based on the ICMP
protocol. \Luc{To scan a network, an attacker sends a set of ICMP Echo requests addresed to a range of IP addresses in the network and sees which one responds to the request. This allow the attacker to know which machines are active in the network, then it can choose one of them to attack.}

>>>>

\Mar{@Lucas/Guilheme, há algo o que remover? talvez ``window:64''?
  Qual a correspondencia de ``flags:S,12'' com ``flags:S''? Por favor,
  respondam isto logo.}  \Gui{}

@@

Finally, \tname{} ranks the inferred rules according to heuristics
extracted from a database of existing \tname{} rules. One example
heuristic is \Fix{...informa um exemplo concreto que
  vc. usaram...}. Instead of traffic, this step looks for the
structure of existing rules. The list below shows the rule options for
the top-5 rules \tname{} produces for this attack.

\Mar{listem 5 primeira regras neste caso}

\subsection{Active Recnnaissance}

Active reconnaissance is a method used by malicious individuals to
collection information about a computing system to determine potential
vulnerabilities. Active reconnaissance is a preliminary step towards
an actual attack. The most popular technique is to ``scan'' open ports
in a host. A Ping Scan is a very common type of port scan based and it
is based on the ICMP protocol. \Mar{@Lucas, acima falamos de
  porta. Abaixo nao falamos de porta, apenas de maquina. Vc. pode ser
  mais especifico? ->}To scan a network, an attacker sends a several
ICMP Echo requests addressed to a range of IP addresses in the network
and checks which ones respond to the requests. This allow the attacker
to know which machines are active in the network, then it can choose
one of them to attack.

@@
